---
title: "World Development Indicators 2022"
author: "Angela Xie"
date: "2024-10-04"
format:
  revealjs:
    theme: sky
    transition: zoom
---

# World Development Indicators 2022

By Angela Xie

---

## GDP Per Capita for top 10 countries


```{r}

# Load the dataset using preferred programming language
df <- read.csv("wdi.csv")

# Sort the dataset by GDP per capita and select the top 10 countries
top10_gdp <- df[order(-df$gdp_per_capita), ][1:10, ]

# Create a bar chart for the top 10 countries by GDP per capita
barplot(
  height = top10_gdp$gdp_per_capita,
  names.arg = top10_gdp$country,
  col = "pink",
  las = 2, 
  main = "Top 10 Countries by GDP per Capita",
  xlab = "Country",
  ylab = "GDP per Capita (USD)"
)
```



---

## Literacy Rate vs GDP Growth Rate

```{r}
# Scatter plot of Literacy Rate vs GDP Growth Rate 
plot(
  df$adult_literacy_rate, df$gdp_growth_rate,
  xlab = "Adult Literacy Rate (%)",
  ylab = "GDP Growth Rate (%)",
  main = "Adult Literacy Rate vs GDP Growth Rate",
  col = "blue",
)
```

---

## Summary Table

```{r}
cat(
  "Indicator                | Mean      | Range\n",
  "------------------------ | --------- | ----------------\n",
  "GDP Per Capita            |", round(mean(df$gdp_per_capita, na.rm = TRUE), 2), "|", min(df$gdp_per_capita, na.rm = TRUE), "-", max(df$gdp_per_capita, na.rm = TRUE), "\n",
  "GDP Growth Rate           |", round(mean(df$gdp_growth_rate, na.rm = TRUE), 2), "|", min(df$gdp_growth_rate, na.rm = TRUE), "-", max(df$gdp_growth_rate, na.rm = TRUE), "\n",
  "Adult Literacy Rate       |", round(mean(df$adult_literacy_rate, na.rm = TRUE), 2), "|", min(df$adult_literacy_rate, na.rm = TRUE), "-", max(df$adult_literacy_rate, na.rm = TRUE), "\n"
)

```


---

## Conclusion

- The analysis revealed the top 10 countries by GDP per capita. These countries are the wealthiest in terms of average income per person.
- However, the correlation between **GDP growth** and **adult literacy rate** appears to be weak, suggesting that higher literacy does not always translate into higher economic growth.
- This insight highlights that while GDP per capita can indicate wealth, other factors like education may not directly influence GDP growth in a linear manner.